Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex

\subsection{IFC-aware language features}
\label{sec:extensions:labeled}

\subsubsection{Labeled objects}

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

>>>>

\subsection{IFC language features}
\label{sec:extensions:labeled}

\paragraph{Labeled values}
%{
%format Lb = "\textbf{Labeled}"
In traditional language-based dynamic IFC systems, a label is
associated with values.
%
Hence, a program that, for example, simply writes labeled messages to
a labeled log can operate on both public and sensitive values.
%
In its simplest form, our coarse grained system requires that the
current label of a task be at least at the level of the sensitive data
to reflect the fact that such data is in scope.

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{Hritcu:2013:YIB:2497621.2498098, lio}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
Similarly, when creating labeled values the label |il| must be above
the current label; otherwise |il| cannot be said to protect the value.
%
(Importantly, we assumes that the |Lb| constructor cannot be accessed
directly to construct or destruct such values without label checks.)
%
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%}

\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

### 2014-03-02 paper/retrofit.tex

Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
operational semantics and combine it with an \textit{{\color{blue} information
flow control language}}.  While our technique will be indifferent to the
actual target language, for concreteness we give a simple, untyped,
ML-like language to illustrate some examples, as well as express
how the language should be prepared for interoperability
in the style of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220}.
We then equip this target language with primitives for implementing dynamic
information control in the style of LIO~\cite{lio}, which we will
describe in more detail shortly.

@@

\subsection{Target language: Mini-ML}

In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
mutable references, prepared for combination with an
information flow control language.  The presentation is standard, but it
is worth paying some attention to the Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
operational semantics of the system.  Our language defines an evaluation
context |tE|; however, the evaluation rules have been expressed in terms
of a different evaluation context |curlyRedE|,
following the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
semantics of multiple languages.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state |tS|, some evaluation context |tE|,
some expressions |te|, some set of values |tv| and a \emph{deterministic}
reduction relation on full configurations $|tS| \times |tE| \times |te|$.

@@

\caption{Simple ML-like language |targetLangML|}
\label{fig:ml}
\end{figure}

@@

%   \begin{figure}
%   Typing judgment: $|tyrule tG tS te tty|$
%   \begin{mathpar}
%   \inferrule[T-ty-address]
%   {}
%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
%   \end{mathpar}

%   \caption{Selected typing rules for ML-like language}
%   \label{fig:ml-typing}
%   \end{figure}

>>>>

Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
operational semantics and combine it with an \textit{{\color{blue} information
flow control language}}. While our technique will be indifferent to the
actual target language, for concreteness we give a simple, untyped lambda calculus to illustrate some examples, as well as express
how the language should be prepared for interoperability
in the style of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220}.
We then equip this target language with primitives for implementing dynamic
information control in the style of LIO~\cite{lio}, which we will
describe in more detail shortly.

@@

\subsection{Target language: Mini-ES}

In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
mutable references, prepared for combination with an
information flow control language.  The presentation is standard, but it
is worth paying some attention to the Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
operational semantics of the system.  Our language defines an evaluation
context |tE|; however, the evaluation rules have been expressed in terms
of a different evaluation context |curlyRedE|,
following the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
semantics of multiple languages.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state |tS|, some evaluation context |tE|,
some expressions |te|, some set of values |tv| and a \emph{deterministic}
reduction relation on full configurations $|tS| \times |tE| \times |te|$.

@@

\caption{Simple untyped lambda calculus |targetLangML|}
\label{fig:ml}
\end{figure}

@@
